### 2020-07-03 chapters/validation.tex
Validation conclusions

All the synthetic datasets used throughout this Section are a time-series where at each time-step we sample uniformly from a fixed distribution, \textit{i.e.} there are no time correlations in the used datasets. The reference dataset R1 used in this first experiment contained a single feature that followed a normal distribution with mean $\mu=10$ and standard deviation $\sigma=2$ for the 5 million rows of the dataset. Figure \ref{fig:timeseries-r1} shows the time-series of the single feature in dataset R1. The dataset processed in the streaming phase (\textit{i.e.} the target dataset) was generated with a size of 5 million events and a single feature. For the first half, \textit{i.e.}, for the first 2.5 million events, the feature followed a normal distribution with mean $\mu=10$ and standard deviation $\sigma=2$, like the reference dataset. For the other half, we changed the generating distribution to be a continuous uniform one with lower bound $a=100$ and upper bound $b=200$. Figure \ref{fig:timeseries-t1} shows the time-series of the single feature in the target dataset T1 where we see the abrupt change in feature values.
\begin{center}
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/01-reference.pdf}
  \captionof{figure}{Time-series for dataset R1}
  \label{fig:timeseries-r1}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/01-target.pdf}
  \captionof{figure}{Time-series for dataset T1}
  \label{fig:timeseries-t1}
\end{minipage}
\end{center}

@@

\section{Conclusions}

With this set of experiments

>>>>

All the synthetic datasets used throughout this section are a time-series where at each time-step we sample uniformly from a fixed distribution, \textit{i.e.} there are no time correlations in the used datasets. The reference dataset R1 used in this first experiment contained a single feature that followed a normal distribution with mean $\mu=10$ and standard deviation $\sigma=2$ for the 5 million rows of the dataset. Figure \ref{fig:timeseries-r1} shows the time-series of the single feature in dataset R1. The dataset processed in the streaming phase (\textit{i.e.} the target dataset) was generated with a size of 5 million events and a single feature. For the first half, \textit{i.e.}, for the first 2.5 million events, the feature followed a normal distribution with mean $\mu=10$ and standard deviation $\sigma=2$, like the reference dataset. For the other half, we changed the generating distribution to be a continuous uniform one with lower bound $a=100$ and upper bound $b=200$. Figure \ref{fig:timeseries-t1} shows the time-series of the single feature in the target dataset T1 where we see the abrupt change in feature values.
\begin{center}
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/01-reference.pdf}
  \captionof{figure}{Time-series for dataset R1}
  \label{fig:timeseries-r1}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/01-target.pdf}
  \captionof{figure}{Time-series for dataset T1}
  \label{fig:timeseries-t1}
\end{minipage}
\end{center}

@@

\section{Conclusions}
In this section, we summarize our experimental tests, results and found issues.

We began by performing single-feature analysis on synthetic data. The results obtained with this set of experiments were what we expected, in the sense that the artificially introduced anomalies in the datasets were all correctly reported.

Still working with synthetic data, we performed our first multi-feature analysis. In this scenario, we applied the Holm-Bonferroni multiple test correction to the p-values of each hypothesis. Once again, each feature was correctly reported as divergent at the timestamps where we changed the underlying generating distribution.

Finally, we moved on to real data. Due to time constraints and the scope of this thesis, we experimented only with data from one merchant. The results with real data were not satisfactory. In our first experiment with real data, we ran our algorithm with what we thought was an ideal set of parameters and in return produced a lot of alarms. A close analysis of the reference and target time-series of each feature revealed that some alarms indeed made sense, as this dataset contained a lot of drift. In our last experiment, we attempted to reduce concept drift to a maximum by using the same period as reference and target. To our surprise, we still produced a large number of long lasting alarms. We defer the investigation of the root cause of the problem to future work and leave a few untested hypothesis as solutions for this issue.
